\documentclass[11pt]{article}

\usepackage{amssymb,amsmath}
\usepackage{fullpage}
\usepackage{hyperref} % must be last usepackage


\begin{document}

\begin{center}
  \large
  \textbf{Minitab Tips} %\\
%  STAT-UB.0103 -- Statistics for Business Control and Regression Models
\end{center}


\section*{Running Minitab}


You can run Minitab for free from your home computer through Apps@Stern at
\begin{center}
  \url{http://apps.stern.nyu.edu}
\end{center}
To use this site, you log on with your Stern
account. If you do not have a Stern account, you can get one by visiting
\url{http://start.stern.nyu.edu}; all students enrolled in this class are
eligible for a Stern account, even non-Stern students.


When you first visit Apps@Stern, you may have to install the Citrix plugin.
After this, when you log on, you should see a set of program icons, one of
which is for Minitab. Click this icon to start a Minitab session. If any
dialog windows pop up, click ``Ok'' with the default options selected. Ignore
any error messages.

\textbf{Note:} Many students have reported problems with running the
Apps@Stern version of Minitab using Chrome and Firefox.  The website
\begin{center}
\url{http://www.jasonsamuel.com/tag/citrix-ica-client-plugin-firefox/}
\end{center}
may be helpful if you are using Firefox.  Alternatively, try using
Safari~(Mac) or Internet Explorer~(Windows).



\section*{Opening files}

\begin{enumerate}

\item First you have to download the file to your computer.  
Right-click on the link to the file, and then choose ``Save Link As\ldots'' or
control-click on the link and choose ``Download Linked File As\ldots''.

\item Next start Minitab.  From Minitab, choose \textit{File $\Rightarrow$
  Open Worksheet}.  \textbf{Important:} do not use \textit{File $\Rightarrow$
  Open Project}.

\item You may get a message like ``This operation has been cancelled due to
  restrictions in effect on this computer.''  Click ``Ok''.

\item You may have to change the ``Files of type'' box before you can see the
file.  By default, only MTW files will be visible. Most data files used in this
course will be of type CSV.

\item \textbf{Important:} If you are using Apps@Stern, change the directory
  for ``Look in:'' to
  Computer~$\to$ C\$ (\textbackslash\textbackslash Client) (V:).  

\item Find the file saved on your home computer.
  On a Mac, you will likely need to navigate through the
  ``Users'' folder to find your file.

\end{enumerate}



\section*{Printing plots}

\begin{enumerate}

\item First, you have to convert the plot to an image file on your computer.
Make sure the plot is selected, then choose \textbf{File $\Rightarrow$ Save
Graph As\ldots}.

\item Under ``Save as type:'' choose ``PNG Color (*.PNG)''.  Many other
formats will also work.

\item If you are using Apps@Stern, under ``Save in'', navigate to 
Computer~$\to$ Local~Disc~(C: \ldots).

\item Choose an appropriate file name and directory.

\item Double-click on the newly-saved image file and print it.  Alternatively,
you can insert the image into a document using your word-processing program.

\end{enumerate}



\end{document}
